Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-06 measurements.tex
Results description for generation size done

In \ref{fig:enc_good_rasp1_gen_gf2}, \ref{fig:enc_good_rasp1_gen_gf256},
\ref{fig:enc_good_rasp2_gen_gf2} and \ref{fig:enc_good_rasp2_gen_gf256};
it can be seen the goodput trends of 5 codes as a function of
the generation size: \ac{RLNC}, \ac{SRLNC} with $d = [0.02,\ 0.1]$
and \ac{TSNC} with two parameters that we mention. The first of them,
$steps$, is the number of density changes in the system, if any.
The number of changes is equal to the number of regions minus 1, making
$steps = \#regions - 1$ and $dep = e$. With these definitions, we first
evaluate \ac{TSNC} with no changes, e.g. $steps=0$ and the two amounts
for dependent packets mentioned earlier. In this way the budget is
either $g + 8$ or $g + 16$. The goal with setting first \ac{TSNC} with
these values is to observe first the sole effect of the budget in the code
since $steps = 0$ implies no density changes during the whole process.
%
\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_v2_encoder_Binary_1600.eps}
        \caption[]%
        {{\small Goodput vs. Generation size for $q = 2$}}    
        \label{fig:enc_good_rasp2_gen_gf2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}  
        \centering 
        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_v2_encoder_Binary8_1600.eps}
        \caption[]%
        {{\small Goodput vs. Generation size for $q = 2^8$}}    
        \label{fig:enc_good_rasp2_gen_gf256}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{0.475\textwidth}   
        \centering 
        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_v2_encoder_Binary_16.eps}
        \caption[]%
        {{\small Goodput vs. Packet size for $q = 2,\ g=16$}}    
        \label{fig:enc_good_rasp2_packet_gf2}
    \end{subfigure}
    \quad
    \begin{subfigure}[b]{0.475\textwidth}   
        \centering 
        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_v2_encoder_Binary8_16.eps}
        \caption[]%
        {{\small Goodput vs. Packet size for $q = 2^8,\ g=16$}}    
        \label{fig:enc_good_rasp2_packet_gf256}
    \end{subfigure}
    \caption[]
    {\small Encoder goodput measurements for the \ac{Raspi} 2} 
    \label{fig:enc_good_rasp2}
\end{figure*}

>>>>

In \ref{fig:enc_good_rasp1_gen_gf2}, \ref{fig:enc_good_rasp1_gen_gf256},
\ref{fig:enc_good_rasp2_gen_gf2} and \ref{fig:enc_good_rasp2_gen_gf256};
it can be seen the goodput trends of 5 codes as a function of
the generation size: \ac{RLNC}, \ac{SRLNC} with $d = [0.02,\ 0.1]$
and \ac{TSNC} with two parameters that we mention. The first of them,
$steps$, is the number of density changes in the system, if any.
The number of changes is equal to the number of regions minus 1, making
$steps = \#regions - 1$ and $dep = e$. With these definitions, we first
evaluate \ac{TSNC} with no changes, e.g. $steps=0$ and the two amounts
for dependent packets mentioned earlier. In this way the budget is
either $g + 8$ or $g + 16$. This means that we tolerate at most 8 or 16
packets regardless of the generation. The goal with setting first
\ac{TSNC} with these values is to observe first the sole effect of the
budget in the code since $steps = 0$ implies no density changes during
the whole process.

For the plots in the mentioned figures from the encoder goodput measurements,
\ac{RLNC} presents the worst performance in terms of goodput and
\ac{TSNC} with $dep = 16$, the best regardless of the \ac{Raspi} model.
Given that the processing time depends in the amount of coded packets
required to create, \ac{RLNC} is the slowest to process since it must
use all of the $g$ original packets. Later, sparse codes process the data
at a larger rate since less packets are being mixed when creating a
coded packet. The caveat of these schemes is that the sparser the code,
the more probable the ocurrences of \ac{l.d.} packets is. So, basically
the sparser the codes, then more overhead due to transmissions of \ac{l.d.}
packets they have since it is more likely to generate the same set of
packets. Excluding the coding coefficients overhead, the overhead due to
transmissions of \ac{l.d.} packets can be very high.
For example, if we consider \ac{TSNC} with $dep=16$ and $g = 16$, the budget
in this case permits to send up to 32 packets which is $2\times$ the generation
size for an overhead of $100\%$ excluding the one from the coding
coefficients. This happens because \ac{TSNC} is allowed to add too much
redundancy in this case, which permits it to use a very low code density $d$.
For \ac{RLNC} this is not the case, since the occurrence of \ac{l.d.} coded
packets is low. Even for $GF(2)$, the average amount of redundancy has proven
to be 1.6 packets after $g$ have been transmitted.

%
\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_v2_encoder_Binary_1600.eps}
        \caption[]%
        {{\small Goodput vs. Generation size for $q = 2$}}
        \label{fig:enc_good_rasp2_gen_gf2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_generation_size_Rasp_v2_encoder_Binary8_1600.eps}
        \caption[]%
        {{\small Goodput vs. Generation size for $q = 2^8$}}
        \label{fig:enc_good_rasp2_gen_gf256}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_v2_encoder_Binary_16.eps}
        \caption[]%
        {{\small Goodput vs. Packet size for $q = 2,\ g=16$}}
        \label{fig:enc_good_rasp2_packet_gf2}
    \end{subfigure}
    \quad
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.15\textwidth]{images/23_07_2015/goodput_vs_symbol_size_Rasp_v2_encoder_Binary8_16.eps}
        \caption[]%
        {{\small Goodput vs. Packet size for $q = 2^8,\ g=16$}}
        \label{fig:enc_good_rasp2_packet_gf256}
    \end{subfigure}
    \caption[]
    {\small Encoder goodput measurements for the \ac{Raspi} 2}
    \label{fig:enc_good_rasp2}
\end{figure*}
